\documentclass[11pt]{article}
\begin{document}

\section{Intro}
    Moore's Law
    Bell's Law: Something New every decade. A new class of thing every 10 years

    Sense. Compute. Store. Communicate. However... There's limited energy!

    Monitoring...
    \begin{itemize}
        \item Space: Agriculture, volcanoes, etc
        \item Things: Habitat, animals, people (body networks, dexternet), structures
    \end{itemize}

    Tmote Sky: The primary use of energy is for Tx/Rx

    Sensor Categories:
    \begin{itemize}
        \item Chemical \
            Particulate \
            PH \
            Molarity \
            Redox Potential
        \item Environmental \
            Barometer \
            Thermometer
        \item Mechanical \
            Accel \
            Gyro \
            Flow \
            Seizmic
        \item EM \
            Photovoltaic
            RF \
            hall effect (magnetic field)
    \end{itemize}

    Application Categories:
    \begin{itemize}
        \item Structural Health Monitoring \
            Earth Dams \
            Bridges, pipes, buildings
        \item Positional \
            Alarm \
            Cellular \
            GPS \
            New: traffic flow control
        \item Robotics \
            Modular swarms \
            Control Systems \
            Robot flow control
        \item Environmental Control + Monitoring \
            Weather prediction \
            Climate / Weather prediction and modelling \
            Polluction \
            Wildfire prevention
        \item Industrial + Manufacturing \
            Assembly Lines and control \
            Automated visual inspection \
            Inventory management
        \item Scientific Phenomenon
        \item social improvements \
            Crowdsourced weather \
            P2P cell communication/relay \
            Ala Carte Garbage
    \end{itemize}

    Arduino Fio
    \begin{itemize}
        \item MiniUSB ONLY charges
        \item Digital IO
        \item Analog Input only
        \item 2 sets of GND + 3.3v
        \item AREF is the reference for Analog to Digital conversion (AtoD)
        \item CTS: Clear to Send pin
        \item DTR: Sleep pin. Note: needs to be ready to sleep

        \item When programming XBee, you can only program one at a time. Use the programming radio (USB dongle) to program over XBee 802.15.4 Series 1
        \item Default transparent mode. Serial line replacement. Send/Receive ASCII at application level. Don't need to mess with packetization (header, packet, checksum)
        \item Limited addressing: unicast OR broadcast
        \item Advanced features: Sleeping radio, API for messaging, node discovery and coordination, collision avoidance options, RSSI, ACKs, dropped packets, etc...

        \item Arduino IDE
        \item Implement void setup() and void loop()
        \item Serial.begin(57600); \& Serial.println(cstr); delay(ms);
        \item pinMode(13, OUTPUT | INPUT); \& digitalWrite(13, HIGH | LOW); 13 = pin number
        \item int x = digitalRead(13);
    \end{itemize}

    Computer Networks Introduction
    \begin{itemize}
        \item Tiered data transfer setup
        \item TCP
        \item OSI Model
        \item RFCs
    \end{itemize}

\end{document}
